Plots for Latent Hawkes Paper

### 2020-11-18 output_scripts/Paper_Plots.Rmd
improving plots

slides_plots <- FALSE
current_cohort <- 5
```

```{r load_packages, include=FALSE}

@@

## Figure 4a Recover Latent Ranks
```{r fig-4a}
sim_data_path <- "../output/sims/sims_m3_dc/"

@@

    if(m==3){
      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
    }
  }
  ## bottom
  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
        cex=2.4)
  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.7,
        at=0.5)
  ## top
  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=3,
        at=0.5, font=2)
  ## left
  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
        at=c(0:2)/3+0.15,
        cex=2, las=2)
}

@@

```{r fig4b-recover-latent-states}
y.ub <- c(17,17,17)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(50,50,50)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

## top
mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.5)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.5)
```

@@

```{r fig5-residual-ks, fig.height=7}
cols_plot <- viridis::viridis(4)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=rep(0.2,4),oma=c(2.4,2.4,0.5,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04,col=cols_plot[1],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,col=cols_plot[2],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,col=cols_plot[3],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,col=cols_plot[4],border=NA)
        text(c(0.43,0.58,0.61,0.4),seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j],KS_model2_array[,i,j],
              KS_model3_array[,i,j],KS_true_array[,i,j])
      Type <- c(rep(1,n_sim),rep(2,n_sim),rep(3,n_sim),rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")#names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim}
sim_files <- list.files(here("output", "rank_sims",
                             "sims_m3_dc_isi_sparse"))

@@

sim_data %>% 
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + geom_boxplot(aes(fill = Method)) +
  scale_fill_manual(values = viridis::viridis(6)) +
  labs(y = "Rank Correlation") + theme_bw()
```

@@

```{r fig-8a-frob-norm-cohort5}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 150) + # aren't infinite but >150 and <200
  NULL
p3
```

@@

```{r fig-8b-frob-norm-all-cohorts}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm))

>>>>

slides_plots <- FALSE
current_cohort <- 5

@@

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=4,fig.width=8}
sim_data_path <- "../output/sims/sims_m3_dc/"

@@

    if(m==3){
      text(text.x.adj[j],text.y[j],text.x[j],cex=2.4)
    }
  }
  ## bottom
  mtext(text=expression(f[1],f[2],f[3],f[4],f[5]), side=1, line=2.4, outer=TRUE, 
        at=c(1:length(object_par$f_vec_1))/length(object_par$f_vec_1)-0.1,
        cex=2)
  mtext(text="Latent rank variables", side=1, line=5.3, outer=TRUE, cex=2.25,
        at=0.5)
  ## top
  mtext(text="(a)", side=3, line=0, outer=TRUE, cex=2.5,
        at=0.5, font=2)
  ## left
  mtext(text=rev(c("C-HP  ","C-DCHP","C-MMHP")), side=2, line=0.5, outer=TRUE, 
        at=c(0:2)/3+0.15,
        cex=1.75, las=2)
}

@@

```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
y.ub <- c(17,17,17)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(50,50,50)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

## top
mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)
```

@@

```{r fig5-residual-ks, fig.height=7}
cols_plot <- viridis::viridis(4)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=c(0.2,0.2,0.2,0.2),oma=c(2.4,2.4,2.9,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04,col=cols_plot[1],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,col=cols_plot[2],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,col=cols_plot[3],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,col=cols_plot[4],border=NA)
        text(c(0.43,0.58,0.61,0.4),seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j],KS_model2_array[,i,j],
              KS_model3_array[,i,j],KS_true_array[,i,j])
      Type <- c(rep(1,n_sim),rep(2,n_sim),rep(3,n_sim),rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")#names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)
mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim, fig.height=7}
sim_files <- list.files(here("output", "rank_sims",
                             "sims_m3_dc_isi_sparse"))

@@

sim_data %>% 
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + geom_boxplot(aes(fill = Method)) +
  scale_fill_manual(values = viridis::viridis(6)) +
  labs(y = "Rank Correlation") + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") + ggtitle("(b)")
```

@@

```{r fig-8a-frob-norm-cohort5, fig.width=8,fig.height=4}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  #mutate(norm = min(norm,60)) %>%
  # rename(Method = method) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 150) + # aren't infinite but >150 and <200
  NULL
p3 + labs(fill = "Method")
```

@@

```{r fig-8b-frob-norm-all-cohorts,fig.width=8,fig.height=4}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm))
